Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-09 introduction.tex
Changing optical to EM
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1000 ccdd05d5-56c1-461a-bf98-85f6876523b4

In the era of first-generation detectors, the \GW{} community initiated a
project to send alerts when potential \GW{} transients were observed in
order to trigger followup observations by optical telescopes.  The best
demonstrated latencies were on the order of 1 hour%
~\citep{HugheyGWPAW2011}, which was an important
achievement, but far too late to catch prompt \EM{}
emission. In order to extract the maximum science from Advanced \LIGO{}
\CBC{} events, we have the ambition of reporting \GW{} candidates not minutes
\emph{after} the merger, as has already been accomplished, but seconds
\emph{before}.

>>>>

In the era of first-generation detectors, the \GW{} community initiated a
project to send alerts when potential \GW{} transients were observed in
order to trigger followup observations by \EM{} telescopes.  The best
demonstrated latencies were on the order of 1 hour%
~\citep{HugheyGWPAW2011}, which was an important
achievement, but far too late to catch prompt \EM{}
emission. In order to extract the maximum science from Advanced \LIGO{}
\CBC{} events, we have the ambition of reporting \GW{} candidates not minutes
\emph{after} the merger, as has already been accomplished, but seconds
\emph{before}.
